Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-09-07 paper/sections/introduction.tex
[ paper ] fixing some mistakes.

In this paper, we describe the integration of \Metis prover with the
proof assistant \Agda by parsing \TSTP derivations to generate \Agda
proof-terms. We structure the paper as follows. In section
\ref{sec:metis-language-and-proofs} we briefly introduce the \Metis
prover. In section \ref{sec:proof-reconstruction}; we present our
approach to reconstruct proofs deliver by \Metis in \Agda. We list
related work in proof reconstruction in section
\ref{sec:related-work} In section~\ref{sec:conclusions}, we discuss
some limitations, advantages, and disadvantages with other similar
proof reconstruction tools and conclusions for ending up with the
future work.

>>>>

In this paper, we describe the integration of \Metis prover with the
proof assistant \Agda by parsing \TSTP derivations to generate \Agda
proof-terms. We structure the paper as follows. In section
\ref{sec:metis-language-and-proofs}, we briefly introduce the \Metis
prover. In section \ref{sec:proof-reconstruction}; we present our
approach to reconstruct proofs deliver by \Metis in \Agda. We list
related work in proof reconstruction in section
\ref{sec:related-work}. In section~\ref{sec:conclusions}, we discuss
some limitations, advantages, and disadvantages with other similar
proof reconstruction tools and conclusions for ending up with the
future work.

### 2017-09-07 paper/sections/metis-language-and-proofs.tex
[ paper ] fixing some mistakes.

\name{Isabelle/HOL} incorporated \Metis as a macro-step
reconstruction tool for explaining proof steps (usually \CNF goals)
replied from other \ATPs like \name{CVC4}, \name{Vampire}, or
\name{Z3} (more details in Ref.~\cite{paulson2007source}).
In \cite{Farber2015}, \Metis was used to provide a tactic for
\name{HOL Light}; this tactic challenges others like \name{MESON}
tactic or the \name{leanCoP} tactic that reconstructs proofs
delivered by \name{leanCoP}~\cite{Farber2016}.

@@

We noted in \TSTP derivations that \Metis do not take into account
some inference rules for the \Metis' official documentation; we
refer to the \Metis' logic kernel.
Besides the six \Metis' inference rules from the Fig.
\ref{fig:metis-inferences}, its proof-objects, the \TSTP
derivations, exhibit an entirely different set of rules.

For instance, for the propositional logic fragment without equality,
we know only three rules are valid from the \Metis' Logic Kernel:
\emph{assume}, \emph{axiom}, and \emph{resolve}. Nevertheless, as we
observed in \TSTP derivations, for such a propositional fragment,
\Metis uses in his deductions steps, six rules where only the
\emph{resolve} inference persists from the original list. In the
case of \resolve, it differs from its original version since, in
\TSTP, this rules comes with an argument, a literal. The other
undocumented rules found in \TSTP derivations are: \canonicalize,
\clausify, \conjunct, \negate, \simplify, and \strip.

This lack of the \Metis' documentation was an important matter for
us in the proof reconstruction and certainty for other implementors
(see a comment related on the presenting of \name{Sledgehammer}
in \cite{paulson2007source} and \cite{Farber2015}). We faced
the ambiguity and lack of clearness of some rules like \canonicalize
or \simplify. For example, we believe that with these last
inferences, \Metis summarized many essential steps in the conversion
or deduction from one formula or a list of formulas to another.
That is inconvenient since, our proof reconstruction approach needs
take into account any assumption or consideration as ordering for
literals, application of simplification theorems, reductions, among
other valid transformations.

@@

In this part, our main purpose consists of giving a response to
these rules looking at the \Metis' source code while inspecting a
representative set of solutions of \CPL problems
\cite{Prieto-Cubides2017}generated by \Metis.
This is an attempt to fulfill the \Metis's documentation,
describing our understanding of each rule, to later on in section
\ref{sec:proof-reconstruction}, formalize them effectively in \Agda.

@@

\textit{Simplification.}
The \simplify rule is a $n$-ary inference that performs
simplification of definitions. This rule transverses a list of
formulas by applying different theorems (e.g., \emph{modus pones},
\emph{modus tollens}, or \emph{disjunctive syllogism}) including the
list of theorems used by \canonicalize in
Fig.\ref{fig:conjunctive-disjunctive-simpl} and the resolution
theorem of \resolve rule. Moreover, many things happen inside this
\Metis' procedure, and it is somewhat complicated to grasp it
completely.

\end{document}

>>>>

\name{Isabelle/HOL} incorporated \Metis as a macro-step
reconstruction tool for explaining proof steps (usually \CNF goals)
replied from other \ATPs like \name{CVC4}, \name{Vampire}, or
\name{Z3} (more details in Ref.~\cite{paulson2007source}).
In \cite{Farber2015}, \Metis was used to provide a tactic for
\name{HOL Light}; this challenges others like \name{MESON}
or the \name{leanCoP} tactic that reconstructs proofs
delivered by \name{leanCoP}~\cite{Farber2016}.

@@

We noted in \TSTP derivations that \Metis does not take into account
some inference rules for the \Metis' official documentation; we
refer to the \Metis' logic kernel.
Besides the six \Metis' inference rules from the Fig.
\ref{fig:metis-inferences}, its proof-objects, the \TSTP
derivations, exhibit an entirely different set of rules.

For instance, for the propositional logic fragment without equality,
only three rules are valid from the \Metis' Logic Kernel:
\emph{assume}, \emph{axiom}, and \emph{resolve}. Nevertheless, as we
observed in \TSTP derivations, for such a propositional fragment,
\Metis uses in his deductions steps, six rules where only the
\emph{resolve} inference persists from the original list. In the
case of \resolve, it differs from its original version since, in
\TSTP, this rules come with an argument, a literal. The other
undocumented rules found in \TSTP derivations are: \canonicalize,
\clausify, \conjunct, \negate, \simplify, and \strip.

This lack of the \Metis' documentation was an important matter for
us in the proof reconstruction and certainty for other implementors
(see a comment related on the presenting of \name{Sledgehammer}
in \cite{paulson2007source} and \cite{Farber2015}). We faced
the ambiguity and lack of clearness of some rules like \canonicalize
or \simplify. For example, we believe that with these last
inferences, \Metis summarized many essential steps in the conversion
or deduction from one formula or a list of formulas to another as we see in the following example.
\improvement{Add an example showing a deduction where metis do a lot 
between two steps}
That is inconvenient since, our proof reconstruction approach needs
take into account any assumption or consideration as ordering for
literals, application of simplification theorems, reductions, among
other valid transformations.

@@

In this part, our main purpose consists of giving a response to
these rules looking at the \Metis' source code while inspecting a
representative set of solutions of \CPL problems
\cite{Prieto-Cubides2017} generated by \Metis.
This is an attempt to fulfill the \Metis's documentation,
describing our understanding of each rule, to later on in section
\ref{sec:proof-reconstruction}, formalize them effectively in \Agda.

@@

\textit{Simplification.}
The \simplify rule is inference that performs simplification of 
definitions or tautologies over a list of derivations. This rule 
transverses a list of formulas by applying different theorems (e.g.,
\emph{modus pones}, \emph{modus tollens}, or \emph{disjunctive
syllogism}) including the list of theorems used by \canonicalize in Fig.
\ref{fig:conjunctive-disjunctive-simpl} and the resolution theorem of
\resolve rule. Moreover, many things happen inside this \Metis'procedure, 
and it is somewhat complicated to grasp it completely.
\end{document}

### 2017-09-07 paper/sections/proof-reconstruction.tex
[ paper ] major changes, abstract, conclusions was added.
[ paper ] fixing some mistakes.

\subsection{The Translation Method}

Our system (see Fig~\ref{fig:proof-reconstruction-overview}) translates a \verb!TSTP!
file into an \verb!Agda! proof by parsing it with a \verb!Haskell! tool.
This tool reconstructs the proof tree, removing redundancies and
cutting unnecessary steps (see for example repetitions in the derivation shown in
Fig~\ref{fig:metis-example}). The output is \verb!Agda! code.
Then, we use \verb!Agda! as a proof checker to type-check the proof.
If type-checking succeed, then our proof is checked. Else, we have a failure
proof due to three possible factors. First, a soundness bug in the ATP or a bug
in the output printing. Second, a bug in the translation process in our \verb!TSTP! parsing
module, the inner algorithms in the analysis of the proof tree, the pretty printer
module, or a bug in \verb!Haskell!. Lastly, a bug in our proof checker \verb!Agda!.

% ---------------------------------------------------------------------------

\subsection{Reconstruction Work-flow}

\begin{figure}
\begin{tikzpicture}
\node[text width=2cm, align=center](problem) at (0,0)
  {CPL \\ Problem};

\node[right = 1.2cm of problem, text width=2cm, align=center]
  (tptp){\verb!TPTP! \\ Problem};

\node[right= 1.2cm of tptp, text width=2cm, align=center]
   (metis) {\verb!Metis! \\ Prover};

\node[right= 1.2cm of metis, text width=2cm, align=center, inner sep=10pt]
   (tstp) {\verb!TSTP! \\ Derivation};

\node[below= 0.5cm of tstp, text width=2cm, align=center, inner sep=10pt]
  (athena) {\verb!Haskell! \\ Traslator};

\node[left = 1.2cm of athena, text width=2cm, align=center]
   (agdafile) {\verb!Agda! \\ Proof};

\node[left = 1.2cm of agdafile, text width=2cm, align=center]
   (agda) {Proof Checker};

\node[below = 0.5cm of problem, text width=2cm, align=center]
   (verified) {Checked};

\node[below = 0.5cm of verified, text width=2cm, align=center]
   (failure) {Error};

@@

% ---------------------------------------------------------------------------

\subsection{Proof Cheker}
\label{ssec:agda}\

\verb!Agda! is an interactive system for constructing proofs and programs,
based on Martin-L\"{o}f's type theory and extended with records, parametrised
modules, among other features.
One of the main strengths of \verb!Agda! is its support for writing proofs,
which we shall call \verb!Agda!'s proof engine. It consists of: support for
inductively defined types, including inductive families, and function
definitions using pattern matching on such types, normalisation during type-
checking, commands for refining proof terms, coverage checker and termination
checker.
The inductive approach for representing classical propositional logic
is better because we benefit from \verb!Agda!'s proof engine and its Unicode
support that allows us writing proofs similar as we find in math text books.

% ---------------------------------------------------------------------------

\subsection{LCF-Style Theorem Proving}
\label{ssec:lcf-style-theormem-proving}

A propositional formula is a experssion of indivisible propositional atoms,
logical connectives $\{\wedge, \vee, \Rightarrow, \Leftrightarrow, \neg\}$
and logic constants $\{\top, \bot\}$.
In \verb!Agda!, we define the formula
as an inductive type using the keyword \texttt{data} and including every
connective as a constructor. We represent propositional formulas with
\verb!Prop! data type using the following definition.

%an extension of the syntax definition used in \cite{Altenkirch2015}.

\begin{verbatim}
data Prop : Set where
  Var              : Fin n → Prop
  ⊤                : Prop
  ⊥                : Prop
  _∧_ _∨_ _⇒_ _⇔_  : (φ ψ : Prop) → Prop
  ¬_               : (φ : Prop)   → Prop
\end{verbatim}

On the other hand, we represent theorems in CPL using an abstract data type
to implement a natural deduction calculus.

\begin{verbatim}
data _⊢_ : (Γ : Ctxt)(φ : Prop) → Set where
\end{verbatim}

The sequents  $\Gamma \vdash \phi$ represent theorems,
where $\Gamma$ is a set of premises and $\phi$ is the
sequent's conclusion. Strictly speaking, we define the set of premises
$\Gamma$ with \verb!List! data type
% \footnote{We use the \verb!Agda! standard library's implementation of the List data type.}.

Our CPL system define all inference rules for intuitonistic propositional logic
(see Fig.~\ref{fig:theorem-constructors}) as constructors of the theorem
data type, and we postulate the principle of the excluded middle (PEM).

\begin{verbatim}
postulate  PEM : ∀ {Γ} {φ} → Γ ⊢ φ ∨ ¬ φ
\end{verbatim}

\begin{figure}
\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{}
\RightLabel{\scriptsize\tt assume $\varphi$}
\UnaryInfC{$\Gamma , \varphi \vdash \varphi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\RightLabel{\scriptsize\tt weaken $\psi$}
\UnaryInfC{$\Gamma , \psi \vdash \varphi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{}
\RightLabel{\scriptsize\tt $\top$-intro}
\UnaryInfC{$\Gamma \vdash \top$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \bot$}
\RightLabel{\scriptsize\tt $\bot$-elim $\varphi$}
\UnaryInfC{$\Gamma \vdash \varphi$}
\end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma , \varphi \vdash \bot$}
\RightLabel{\scriptsize\tt $\neg$-intro}
\UnaryInfC{$\Gamma \vdash \neg \varphi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg \varphi$}
\AxiomC{$\Gamma \vdash \varphi$}
\RightLabel{\scriptsize\tt $\neg$-elim}
\BinaryInfC{$\Gamma \vdash \bot$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\AxiomC{$\Gamma \vdash \psi$}
\RightLabel{\scriptsize\tt $\wedge$-intro}
\BinaryInfC{$\Gamma \vdash \varphi \wedge \psi$}
\end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi \wedge \psi$}
\RightLabel{\scriptsize\tt $\wedge$-proj$_1$}
\UnaryInfC{$\Gamma\vdash \varphi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi \wedge \psi$}
\RightLabel{\scriptsize\tt $\wedge$-proj$_2$}
\UnaryInfC{$\Gamma\vdash \psi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\RightLabel{\scriptsize\tt $\vee$-intro$_1$ $\psi$}
\UnaryInfC{$\Gamma \vdash \varphi \vee \psi$}
\end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \psi$}
\RightLabel{\scriptsize\tt $\vee$-intro$_2$ $\varphi$}
\UnaryInfC{$\Gamma \vdash \varphi \vee \psi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma ,\varphi \vdash \gamma $}
\AxiomC{$\Gamma , \psi  \vdash \gamma$}
\RightLabel{\scriptsize\tt $\vee$-elim}
\BinaryInfC{$\Gamma , \varphi \vee \psi \vdash \gamma$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma , \varphi \vdash \psi$}
\RightLabel{\scriptsize\tt $\Rightarrow$-intro}
\UnaryInfC{$\Gamma \vdash \varphi \Rightarrow \psi$}
\end{bprooftree}
%}
\]

\[
%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi \Rightarrow \psi$}
\AxiomC{$\Gamma \vdash \varphi$}
\RightLabel{\scriptsize\tt $\Rightarrow$-elim}
\BinaryInfC{$\Gamma \vdash \psi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma , \varphi \vdash \psi$}
\AxiomC{$\Gamma , \psi \vdash \varphi$}
\RightLabel{\scriptsize\tt $\Leftrightarrow$-intro}
\BinaryInfC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
\end{bprooftree}
%}
\]

\[
%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
\RightLabel{\scriptsize\tt $\Leftrightarrow$-elim$_1$}
\BinaryInfC{$\Gamma \vdash \psi$}
\end{bprooftree}\quad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi$}
\AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
\RightLabel{\scriptsize\tt $\Leftrightarrow$-elim$_2$}
\BinaryInfC{$\Gamma \vdash \psi$}
\end{bprooftree}
%}
\]

\caption{Inference rules for CPL system.}
\label{fig:theorem-constructors}
\end{figure}

% ---------------------------------------------------------------------------

% ---------------------------------------------------------------------------

\subsection{Emulation of Inference Rules in Agda}
\label{ssec:emulating-inferences}

\textit{Normalization.}

\begin{figure}
\[ \scalebox{0.9}{
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi$}

  \UnaryInfC{$\Gamma \vdash \texttt{cnf}~\varphi$}
\end{bprooftree}
\qquad
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi$}
  \UnaryInfC{$\Gamma \vdash \texttt{nnf}~\varphi$}
\end{bprooftree}
\qquad
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi$}
  \UnaryInfC{$\Gamma \vdash \texttt{dnf}~\varphi$}
\end{bprooftree}
}\]
\end{figure}

\begin{figure}
\[%\scalebox{0.9}{
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \wedge \bot$}
  \UnaryInfC{$\Gamma \vdash \bot$}
\end{bprooftree}
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \wedge \top$}
  \UnaryInfC{$\Gamma \vdash \varphi$}
\end{bprooftree}
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \wedge \neg \varphi$}
  \UnaryInfC{$\Gamma \vdash \bot$}
\end{bprooftree}
%}
\]

\[%\scalebox{0.9}{
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \vee \bot$}
  \UnaryInfC{$\Gamma \vdash \varphi$}
\end{bprooftree}
\qquad
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \vee \top$}
  \UnaryInfC{$\Gamma \vdash \top$}
\end{bprooftree}
\qquad
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \vee \neg \varphi$}
  \UnaryInfC{$\Gamma \vdash \top$}
\end{bprooftree}
%}
\]
\end{figure}

\textit{Resolution.}

\begin{figure}
\[%\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\delta_{\phi} := \Gamma \vdash \varphi$}
\AxiomC{$\delta_{\psi} := \Gamma \vdash \psi$}
\RightLabel{\texttt{resolve} $p$}
\BinaryInfC{$\Gamma \vdash$ \texttt{resolve} $\phi\ \psi\ p$}
\end{bprooftree}
%}
\]
% \caption{Resolution in \verb!Metis!.}
\label{fig:resolution-rule}
\end{figure}

\textit{Splitting a conjunct.}
In the following theorem, we see the definition for the \verb!conjunct! rule.
It extracts the $\varphi_i$ conjunct from the conjunction given by $\varphi$.

\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi := \varphi_1 \wedge \cdots\wedge\varphi_i
\wedge\cdots\wedge \varphi_n$}
\AxiomC{$\varphi_i \equiv \psi$}
\RightLabel{\footnotesize\tt conjunct $\psi$}
\BinaryInfC{$\Gamma\vdash\varphi_i$}
\end{bprooftree}
}
\]

\textit{Splitting a goal}

\begin{figure}
\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi_1 \wedge \varphi_2$}
\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\varphi_1) \wedge \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\varphi_2)$}
\end{bprooftree}
}\]

\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi_1 \vee \varphi_2$}
\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\neg \varphi_1 \Rightarrow \texttt{split}~\varphi_2)$}
\end{bprooftree}
}\]

\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \varphi_1 \Rightarrow \varphi_2$}
\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\varphi_2)$}
\end{bprooftree}\qquad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg \neg \varphi$}
\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\varphi)$}
\end{bprooftree}
}\]

\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$ \Gamma \vdash \varphi_1 \Leftrightarrow \varphi_2$}
\UnaryInfC{$\Gamma\vdash\texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\varphi_2) \wedge \texttt{unshunt}~(\varphi_2 \Rightarrow \texttt{split}~\varphi_1)$}
\end{bprooftree}
}\]

\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg \top$}
\UnaryInfC{$\Gamma \vdash \bot$}
\end{bprooftree}\qquad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg \bot$}
\UnaryInfC{$\Gamma \vdash \top$}
\end{bprooftree}\qquad
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg (\varphi_1 \wedge \varphi_2)$}
\UnaryInfC{$\Gamma \vdash \texttt{unshunt} (\varphi_1 \Rightarrow \texttt{split}~ \neg \varphi_2)$}
\end{bprooftree}
}\]

\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg (\varphi_1 \vee \varphi_2)$}
\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\neg \varphi_1) \wedge  \texttt{unshunt}~(\neg \varphi_1 \Rightarrow \texttt{split}~\neg \varphi_2)$}
\end{bprooftree}
}\]

\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg (\varphi_1 \Rightarrow \varphi_2)$}
\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\texttt{split}~\varphi_1) \wedge \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\neg \varphi_2)$}
\end{bprooftree}\qquad
}\]

\[\scalebox{0.9}{
\begin{bprooftree}
\AxiomC{$\Gamma \vdash \neg (\varphi_1 \Leftrightarrow \varphi_2)$}
\UnaryInfC{$\Gamma \vdash \texttt{unshunt}~(\varphi_1 \Rightarrow \texttt{split}~\neg \varphi_2) \wedge \texttt{unshunt}~(\neg \varphi_2 \Rightarrow \texttt{split}~\varphi_1)$}
\end{bprooftree}
}\]
\caption{Split a goal in an equivalent conjunction of subgoals.}
\label{split}
\end{figure}

In the theorems above appear two recursive functions \texttt{unshunt} and \texttt{split}. They have the following definitions.

\begin{verbatim}
unshunt : Prop → Prop
unshunt (φ₁ ⇒ (φ₂ ⇒ φ₃)) = unshunt ((φ₁ ∧ φ₂) ⇒ φ₃)
unshunt (φ₁ ⇒ (φ₂ ∧ φ₃)) = unshunt (φ₁ ⇒ φ₂)) ∧ (unshunt(φ₁ ⇒ φ₃)
unshunt φ                = φ
\end{verbatim}

\begin{verbatim}
split : Prop → Prop
split (φ₁ ∧ φ₂)     = {!!}
split (φ₁ ∨ φ₂)     = {!!}
split (φ₁ ⇒ φ₂)     = {!!}
split (φ₁ ⇔ φ₂)     = {!!}
split (¬ ⊤)         = {!!}
split (¬ ⊥)         = {!!}
split (¬ (φ₁ ∧ φ₂)) = {!!}
split (¬ (φ₁ ∨ φ₂)) = {!!}
split (¬ (φ₁ ⇒ φ₂)) = {!!}
split (¬ (φ₁ ⇔ φ₂)) = {!!}
split (¬ (¬ φ))     = {!!}
split φ₁            = {!!}
\end{verbatim}

...

\textit{Simplification.}

\begin{figure}
\[%\scalebox{0.9}{
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \Leftrightarrow \psi$}
  \AxiomC{$\Gamma \vdash \psi$}
  \RightLabel{\footnotesize\tt $\Leftrightarrow$-elim}
  \BinaryInfC{$\Gamma \vdash \varphi$}
\end{bprooftree}
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \Rightarrow \psi$}
  \AxiomC{$\Gamma \vdash \varphi$}
  \RightLabel{\footnotesize\tt $\Rightarrow$-elim}
  \BinaryInfC{$\Gamma \vdash \psi$}
\end{bprooftree}
\]
\[
\begin{bprooftree}
  \AxiomC{$\Gamma \vdash \varphi \vee \neg \psi$}
  \AxiomC{$\Gamma \vdash \neg \varphi$}
  \BinaryInfC{$\Gamma \vdash \psi$}
\end{bprooftree}
%}
\]

\caption{Additional simplification theorems.}
\label{fig:simplify-rule}
\end{figure}

>>>>

\begin{figure}
\begin{tikzpicture}
\node[text width=2cm, align=center](problem) at (0,0)
  {1. CPL \\ Problem.};

\node[right = 1.2cm of problem, text width=2cm, align=center]
  (tptp){2. \TPTP \\ Problem.};

\node[right= 1.2cm of tptp, text width=2cm, align=center]
   (metis) {3. \Metis \\ Prover.};

\node[right= 1.2cm of metis, text width=2cm, align=center, inner sep=10pt]
   (tstp) {4. \TSTP \\ Derivation.};

\node[below= 0.5cm of tstp, text width=2cm, align=center, inner sep=10pt]
  (athena) {5. \Haskell \\ Traslator.};

\node[left = 1.2cm of athena, text width=2cm, align=center]
   (agdafile) {6. \Agda \\ Proof.};

\node[left = 1.2cm of agdafile, text width=2cm, align=center]
   (agda) {7. Proof Checker.};

\node[below = 0.5cm of problem, text width=2cm, align=center]
   (verified) {8.1 Proof \\ Checked.};

\node[below = 0.5cm of verified, text width=2cm, align=center]
   (failure) {8.2 Error.};

@@
